My title

### 2024-01-23 outputs/paper/paper.qmd
Summary Table
Added a summary statistics table

```{r}
#| echo: false
#| include: true
#| message: false
#| label: fig-totalgraph
#| fig-cap: "Graph showing Total Refugees Over Time"

final_refugees_data |>
  ggplot(mapping = aes(x = Date, y = Total_Refugees)) +
  geom_line() +
  geom_point() +
  theme_minimal() +
  labs(x = "Date (Monthly)", y = "Total Refugees", 
       caption = "Data source: City of Toronto Open Data") +
  scale_x_date(date_labels = "%b %Y", date_breaks = "1 year")
```

```{r}
#| echo: false
#| include: true
#| message: false
#| label: fig-newgraph
#| fig-cap: "Graph showing Trend of New Refugees Over Time"

@@

```{r}
#| echo: false
#| include: true
#| message: false
#| label: fig-percentgraph
#| fig-cap: "Graph showing Trend of Refugees Percentage of Population Over Time"

>>>>

```{r}
#| echo: false
#| include: true
#| message: false
#| label: fig-totalgraph
#| fig-cap: "Graph showing Total Refugees Over Time"
#| fig-pos: H

final_refugees_data |>
  ggplot(mapping = aes(x = Date, y = Total_Refugees)) +
  geom_line() +
  geom_point() +
  theme_minimal() +
  labs(x = "Date (Monthly)", y = "Total Refugees in Shelters", 
       caption = "Data source: City of Toronto Open Data") +
  scale_x_date(date_labels = "%b %Y", date_breaks = "1 year")
```

```{r}
#| echo: false
#| include: true
#| message: false
#| label: Summary Statistics
#| tbl-cap: "Summary Statistics"
#| fig-pos: H

#Based on: https://tellingstorieswithdata.com/05-static_communication.html#tables

## Table of Means ##
summary_mean <- final_refugees_data |>
  summarise(across(c(New_Refugees, Total_Refugees, Percentage_of_Total), 
                   list(mean = mean)))

## Table of SDs ##
summary_sd <- final_refugees_data |>
  summarise(across(c(New_Refugees, Total_Refugees, Percentage_of_Total), 
                   list(sd = sd)))

#Based on: https://www.geeksforgeeks.org/create-table-from-dataframe-in-r/
## Final Table ##
kable(data.frame(
    Metric = c("New_Refugees", "Total_Refugees", "Percentage_of_Total"),
    Mean = c(summary_mean$New_Refugees_mean, summary_mean$Total_Refugees_mean, summary_mean$Percentage_of_Total_mean),
    SD = c(summary_sd$New_Refugees_sd, summary_sd$Total_Refugees_sd, summary_sd$Percentage_of_Total_sd)
))

```

```{r}
#| echo: false
#| include: true
#| message: false
#| label: fig-newgraph
#| fig-cap: "Graph showing Trend of New Refugees Over Time"
#| fig-pos: H

@@

```{r}
#| echo: false
#| include: true
#| message: false
#| label: fig-percentgraph
#| fig-cap: "Graph showing Trend of Refugees Percentage of Population Over Time"
#| fig-pos: H
